Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-04-28 ms.Rmd
Cleaning up script and annotating better. Added in RVE to check non-independence is not an issue

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg)

@@

##########
## Achromatic Contrast - dL
##########
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    coefAIC_display = fixef(ConspicDisplayAC)[3]
    CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

##########
# Chromatic contrast - dS
##########
         ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

@@

##########
## Achromatic Contrast - dL
##########
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
coefAIC_court = fixef(ConspicCourtshipAC)[3]
CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
courship_anovaAC <- anova(ConspicCourtshipAC)

##########
# Chromatic contrast - dS
##########
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)

@@

# First, if predator type varies across populations then we would predcit that whether snake and bird actually are different would depend on the population. For example, if, say, in HAwaii and Kenya birds were equally likely as predators then dL would not vary for birds across populations, but would so for snakes. This is an interaction.

PredatorAC <- lmer(dL ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators_inter <- anova(PredatorAC)

# No support for an interaction, so can drop interaction. Tells us that predation, regardless of whether we are talking snake or bird is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system 
PredatorAC <- lmer(dL ~ Predator + Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators <- anova(PredatorAC)
##########
# Chromatic contrast - dS
##########
PredatorCC <- lmer(dS ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorCC)
anova_predators_interCC <- anova(PredatorCC)

Predator$pred_pop <- with(Predator, interaction(Predator, Population))
PredatorCC_pred_pop <- lmer(dS ~ pred_pop + (1|ID), data = Predator) 
summary(PredatorCC_pred_pop)

hypthesis_test <- glht(PredatorCC_pred_pop, df = 101, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pred_pop = c("snake.Hawaii - snake.Kenya = 0",
                                       "bird.Hawaii  - bird.Kenya = 0",
                                       "snake.Hawaii - bird.Hawaii = 0",
                                       "snake.Kenya  - bird.Kenya = 0")))
summary(hypthesis_test)
CI_hyp_test <- as.data.frame(confint(hypthesis_test)$confint)

@@

##########
# Achromatic Contrast - dL
##########
DispBgrdAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)

DispBgrdAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
summary(DispBgrdAC)
anova(DispBgrdAC_inter, DispBgrdAC)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd)

@@

summary(hypthesis_test_preppop)
p_displ_AC <- as.numeric(summary(hypthesis_test_preppop)$test$pvalues)
CI_dis_AC <- as.data.frame(confint(hypthesis_test_preppop)$confint)
##########
# Chromatic Contrast - dS
##########
DispBgrdCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)

DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
summary(DispBgrdCC)
anova(DispBgrdCC_inter, DispBgrdCC)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
DisplayBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = DisplayBgrd)

hypthesis_test_preppop_CC <- glht(DisplayBgrd_pop_backCC, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppop_CC)
p_displ_CC <- as.numeric(summary(hypthesis_test_preppop_CC)$test$pvalues)
CI_Disp_CC <- as.data.frame(confint(hypthesis_test_preppop_CC)$confint)

@@

CourtshipAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

CourtshipAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
summary(CourtshipAC)
anova(CourtshipAC_inter, CourtshipAC)

CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
CourtshipBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = CourtshipBgrd)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

hypthesis_test_preppopCourtship <- glht(CourtshipBgrd_pop_back, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppopCourtship)
 p_courtship_AC <- as.numeric(summary(hypthesis_test_preppopCourtship)$test$pvalues)
CI_AC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtship)$confint)

##########
# Chromatic - dS
##########
CourtshipCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)
        anova(CourtshipCC)

@@

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(CourtshipCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

# Posthoc comparions
  CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
CourtshipBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = CourtshipBgrd)

# Specific planned comparisons
hypthesis_test_preppopCourtshipCC <- glht(CourtshipBgrd_pop_backCC, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya - Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppopCourtshipCC)
p_courtship_CC <- as.numeric(summary(hypthesis_test_preppopCourtshipCC)$test$pvalues)
CI_CC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtshipCC)$confint)
```

@@

Specifically, we tested the following predictions: 1.) display colouration used in male-male contests and courtship will be more conspicuous to a conspecific in Hawaii than Kenya; 2.) display colouration used in response to an encounter with a bird and snake predator will be more conspicuous to both predator types in Hawai’i than Kenya. 3.) under character release, males will have greater capacity to change colour from a subordinate to a dominant state in Hawai’i compared to Kenya.

We also tested the hypothesis that sensory drive and local adaptation are responsible for driving display coloration. Specifically, we predicted that chameleon display colouration in each population would be more conspicuous within its own signaling environment compared to the other population’s signaling environment. For example, Hawaiian chameleons were historically found in Kenya but under sensory drive and local adaptation they are predicted to be more conspicuous in their current signaling environment, Hawai’i. Likewise, Kenyan chameleons have no history in Hawai’i and are therefore predicted to be more conspicuous within their current signaling environment, Kenya.

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich)

@@

    # Fit the model
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
      summary(ConspicDisplayAC)

    # Get the coefficients, and ANOVA statistics for the paper
          coefAIC_display <- fixef(ConspicDisplayAC)[3]
            CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Display_1_IDs <- Display_1 %>% filter(!is.na(sc_SVL), !is.na(Population)) # filter out misssing data
    robust_ConspicDisplayAC <- coef_test(ConspicDisplayAC, cluster = Display_1_IDs$ID, vcov = "CR2")

##########
# Chromatic contrast - dS
##########
    #Fit the model
         ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + (1|ID), data=Display_1)
         summary(ConspicDisplayCC)

    # Get ANOVA statistics for model for the paper
         anovaConspicDisplayCC <- anova(ConspicDisplayCC)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Display_1_IDs <- Display_1 %>% filter(!is.na(sc_SVL), !is.na(Population)) # filter out misssing data
    robust_ConspicDisplayCC <- coef_test(ConspicDisplayCC, cluster = Display_1_IDs$ID, vcov = "CR2")

@@

  # Fit the model
    ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
    summary(ConspicCourtshipAC)

  # Get model stats for ppaer
       coefAIC_court <- fixef(ConspicCourtshipAC)[3]
         CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
    courship_anovaAC <- anova(ConspicCourtshipAC)

 # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Courtship_IDs <- Courtship %>% filter(!is.na(sc_SVL), !is.na(Population)) # filter out misssing data
    robust_ConspicCourtshipAC <- coef_test(ConspicCourtshipAC, cluster = Courtship_IDs$ID, vcov = "CR2")

##########
# Chromatic contrast - dS
##########

  # Fit the model
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
    summary(ConspicCourtshipCC)

  # Get the ANOVA stats for paper
    courship_anovaCC <- anova(ConspicCourtshipCC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Courtship_IDs <- Courtship %>% filter(!is.na(sc_SVL), !is.na(Population)) # filter out misssing data
    robust_ConspicCourtshipCC <- coef_test(ConspicCourtshipCC, cluster = Courtship_IDs$ID, vcov = "CR2")

@@

# First, if predator type varies across populations then we would predcit that whether snake and bird actually are different would depend on the population. For example, if, say, in Hawaii and Kenya birds were equally likely as predators then dL would not vary for birds across populations, but would so for snakes. This is an interaction.

  # Fit model testing this idea above
  PredatorAC_inter <- lmer(dL ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
  summary(PredatorAC_inter)

  # Get ANOVA stats for reporting in the paper of interaction
  anova_predators_inter <- anova(PredatorAC_inter)

# No support for an interaction. Drop interaction and fit the main effects model. Tells us that predation, regardless of whether we are talking about snakes or birds is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system

  # Fit main effects model
    PredatorAC <- lmer(dL ~ Predator + Population + (1|ID), data = Predator) 
    summary(PredatorAC)

  # Grab the ANOVA summary stats
    anova_predators <- anova(PredatorAC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
    robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")

##########
# Chromatic contrast - dS
##########

    # First, if predator type varies across populations then we would predcit that whether snake and bird actually are different would depend on the population. For example, if, say, in Hawaii and Kenya birds were equally likely as predators then dL would not vary for birds across populations, but would so for snakes. This is an interaction.

    # Fit the interaction model.
    PredatorCC <- lmer(dS ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
    summary(PredatorCC)

    # Get ANOVA statistics for the paper
    anova_predators_interCC <- anova(PredatorCC)

    # Support for an interaction between predator type and population in the chromatic realm. Planned comparisons. First re-fit model
      Predator$pred_pop <- with(Predator, interaction(Predator, Population))
    PredatorCC_pred_pop <- lmer(dS ~ pred_pop + (1|ID), data = Predator) 
    summary(PredatorCC_pred_pop)

    # Conduct hypothesis tests of interest
    hypthesis_test <- glht(PredatorCC_pred_pop, df = 101-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pred_pop = c("snake.Hawaii - snake.Kenya = 0",
                                       "bird.Hawaii  - bird.Kenya = 0",
                                       "snake.Hawaii - bird.Hawaii = 0",
                                    "snake.Kenya  - bird.Kenya = 0")))
    # Get the contrasts, and statistical data for these plannned comparions.
      summary(hypthesis_test)
      CI_hyp_test <- as.data.frame(confint(hypthesis_test)$confint)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
    robust_PredatorCC <- coef_test(PredatorCC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

##########
# Achromatic Contrast - dL
##########

  # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

  # Fit the interaction model
  DispBgrdAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC_inter)

  # Fit the main effect model
  DispBgrdAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC)

  # Doesn't look like an interaction, so test.
  anova(DispBgrdAC_inter, DispBgrdAC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt <- clubSandwich::coef_test(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Planned contrast. Fit the model in a slightly different way
  DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
  DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd)

@@

  # Grab contrast stats for paper
  summary(hypthesis_test_preppop)
  p_displ_AC <- as.numeric(summary(hypthesis_test_preppop)$test$pvalues)
   CI_dis_AC <- as.data.frame(confint(hypthesis_test_preppop)$confint)
##########
# Chromatic Contrast - dS
##########

 # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

   # Fit the interaction model
    DispBgrdCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)
    summary(DispBgrdCC_inter)

    # Fit the main effect model
          DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC)

    # Looks like weak evidence for interaction    
        anova(DispBgrdCC_inter, DispBgrdCC)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC <- clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

    # Planned contrasts. Refit model in slight different form
      DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
    DisplayBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = DisplayBgrd)

    # Conduct hypothesis test, df to get t-distribution, use number of lizards not data points
      hypthesis_test_preppop_CC <- glht(DisplayBgrd_pop_backCC, df = 69-1, 
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

    # Grab the statistics for the paper
      summary(hypthesis_test_preppop_CC)
      p_displ_CC <- as.numeric(summary(hypthesis_test_preppop_CC)$test$pvalues)
      CI_Disp_CC <- as.data.frame(confint(hypthesis_test_preppop_CC)$confint)

@@

 # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

  # Fit the interaction model
    CourtshipAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

  # Fit main effects model
    CourtshipAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
    summary(CourtshipAC)

  # Interaction needed? No
    anova(CourtshipAC_inter, CourtshipAC)

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC <- clubSandwich::coef_test(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

  # Planned contrasts / hypothesis tests. Need to fit model a little differently
    CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
    CourtshipBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = CourtshipBgrd)

  # Hypothesis tests
      hypthesis_test_preppopCourtship <- glht(CourtshipBgrd_pop_back, df = 69-1, 
                                        # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

      summary(hypthesis_test_preppopCourtship)

  # Grab the stats for paper
      p_courtship_AC <- as.numeric(summary(hypthesis_test_preppopCourtship)$test$pvalues)
CI_AC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtship)$confint)

##########
# Chromatic - dS
##########
 # Here, we want to test if the conspicuousness of lizard signals is locally adapted to the specific background of the Kenyan and Hawaiian population. The predcition is simply that, if we were to place a Hawaiian animal against the Kenyan background that it would be far more conspicuous compared to if we place a Kenyan animal in a Hawaiian background.

  # Fit interaction model
    CourtshipCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

  # Fit main effect model
      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)
      anova(CourtshipCC)

@@

  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC <- clubSandwich::coef_test(CourtshipCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

  # Planned comparions
    CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
  CourtshipBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = CourtshipBgrd)

  # Specific planned comparisons, # df to get t-distribution, use number of lizards not data points
      hypthesis_test_preppopCourtshipCC <- glht(CourtshipBgrd_pop_backCC, df = 69-1, 
             linfct = mcp(pop_back = c("Hawaii.Kenya - Hawaii.Hawaii = 0")))

  # Grab summary stats for paper
    summary(hypthesis_test_preppopCourtshipCC)
    p_courtship_CC <- as.numeric(summary(hypthesis_test_preppopCourtshipCC)$test$pvalues)
    CI_CC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtshipCC)$confint)
```

@@
